Placeholder

### 2021-02-16 Paper_Histograms.Rmd
Merged all the sign up per month by sample tibbles and tidied the columns

dat.retro_sign_up <- dat.retro_april_sign_up %>% 
  cbind(dat.retro_may_sign_up,
        dat.retro_june_sign_up,
        dat.retro_july_sign_up,
        dat.retro_august_sign_up,
        dat.retro_september_sign_up)

#Gather the variables
dat.retro_sign_up <- dat.retro_sign_up %>% 
  gather(key = "month", value = "n")

@@

>>>>

@@

```{r Left_join sign-up per month by sampple tibs and tidy}

dat.retro_sign_up <- dat.retro_april_sign_up %>% 
  left_join(dat.retro_may_sign_up,
            by = "Sample_plot")

dat.retro_sign_up <- dat.retro_sign_up %>% 
  left_join(dat.retro_june_sign_up,
            by = "Sample_plot")

dat.retro_sign_up <- dat.retro_sign_up %>% 
  left_join(dat.retro_july_sign_up,
            by = "Sample_plot")

dat.retro_sign_up <- dat.retro_sign_up %>% 
  left_join(dat.retro_august_sign_up,
            by = "Sample_plot")

dat.retro_sign_up <- dat.retro_sign_up %>% 
  left_join(dat.retro_september_sign_up,
            by = "Sample_plot")

#Gather the variables
dat.retro_sign_up <- dat.retro_sign_up %>% 
  gather(key = "month",
         value = "n",
         c(-Sample_plot))
